% Original 24-condition plan and result-availability audit.
\clearpage
\begingroup
\scriptsize
\setlength{\tabcolsep}{2pt}
\renewcommand{\arraystretch}{1.12}
\begin{longtable}{
  >{\raggedright\arraybackslash}p{0.065\linewidth}
  >{\raggedright\arraybackslash}p{0.14\linewidth}
  >{\raggedright\arraybackslash}p{0.17\linewidth}
  >{\raggedright\arraybackslash}p{0.14\linewidth}
  >{\raggedright\arraybackslash}p{0.10\linewidth}
  >{\raggedright\arraybackslash}p{0.25\linewidth}
}
\caption{Original 24-condition plan and result-availability audit.}
\label{tab:original_24_run_audit}\\
\toprule
\textbf{Run} & \textbf{Block} & \textbf{Condition} & \textbf{Result status} & \textbf{Red. (\%)} & \textbf{Audit note} \\
\midrule
\endfirsthead

\multicolumn{6}{l}{\tablename~\thetable\quad continued} \\
\toprule
\textbf{Run} & \textbf{Block} & \textbf{Condition} & \textbf{Result status} & \textbf{Red. (\%)} & \textbf{Audit note} \\
\midrule
\endhead

\midrule
\multicolumn{6}{r}{Continued on next page} \\
\endfoot

\bottomrule
\endlastfoot

R01 & matched hexose bridge & lactose; 55~$^\circ$C; 4~h; +US & available: direct exact & 51.66 $\pm$ 0.81 & Direct match to the planned 24-run condition. \\
R02 & matched hexose bridge & glucose; 55~$^\circ$C; 4~h; +US & available: direct exact & 59.91 $\pm$ 2.62 & Direct match to the planned 24-run condition. \\
R03 & matched hexose bridge & galactose; 55~$^\circ$C; 4~h; +US & available: direct exact & 59.59 $\pm$ 2.33 & Direct match to the planned 24-run condition. \\
R04 & matched hexose bridge & mannose; 55~$^\circ$C; 4~h; +US & available: direct exact & 65.40 $\pm$ 1.76 & Direct match to the planned 24-run condition. \\
R05 & matched hexose bridge & lactose; 60~$^\circ$C; 4~h; +US & available: direct exact & 56.59 $\pm$ 2.57 & Direct match to the planned 24-run condition. \\
R06 & matched hexose bridge & glucose; 60~$^\circ$C; 4~h; +US & available: direct exact & 60.15 $\pm$ 1.52 & Direct match to the planned 24-run condition. \\
R07 & matched hexose bridge & galactose; 60~$^\circ$C; 4~h; +US & available: direct exact & 61.31 $\pm$ 2.99 & Direct match to the planned 24-run condition. \\
R08 & matched hexose bridge & mannose; 60~$^\circ$C; 4~h; +US & available: direct exact & 68.15 $\pm$ 0.69 & Direct match to the planned 24-run condition. \\
R09 & hexose no-ultrasound sentinel & lactose; 55~$^\circ$C; 4~h; no US & available: direct exact & 46.94 $\pm$ 3.30 & Supplemented from ELISA-2026.6.15.xlsx; user confirmed this label denotes the no-ultrasound 55 C 4 h sentinel. \\
R10 & hexose no-ultrasound sentinel & glucose; 55~$^\circ$C; 4~h; no US & available: direct exact & 58.10 $\pm$ 2.31 & Supplemented from ELISA-2026.6.15.xlsx; user confirmed this label denotes the no-ultrasound 55 C 4 h sentinel. \\
R11 & hexose no-ultrasound sentinel & galactose; 55~$^\circ$C; 4~h; no US & available: direct exact & 55.78 $\pm$ 2.51 & Supplemented from ELISA-2026.6.15.xlsx; user confirmed this label denotes the no-ultrasound 55 C 4 h sentinel. \\
R12 & hexose no-ultrasound sentinel & mannose; 55~$^\circ$C; 4~h; no US & available: direct exact & 62.25 $\pm$ 2.62 & Supplemented from ELISA-2026.6.15.xlsx; user confirmed this label denotes the no-ultrasound 55 C 4 h sentinel. \\
R13 & benchmark anchor & lactose; 60~$^\circ$C; 2~h; +US & available: direct exact & 81.52 $\pm$ 2.29 & Source table does not print temperature; user confirmed the condition matches. \\
R14 & benchmark anchor & glucose; 60~$^\circ$C; 2~h; +US & available: direct exact & 70.02 $\pm$ 3.31 & Source table does not print temperature; user confirmed the condition matches. \\
R15 & practical anchor & lactose; 55~$^\circ$C; 3~h; +US & available: direct exact & 61.63 $\pm$ 1.10 & Source table does not print temperature; user confirmed the condition matches. \\
R16 & practical anchor & glucose; 55~$^\circ$C; 3~h; +US & available: direct exact & 70.99 $\pm$ 1.99 & Source table does not print temperature; user confirmed the condition matches. \\
R17 & pentose branch & arabinose; 55~$^\circ$C; 2~h; +US & available: direct exact & 67.50 $\pm$ 2.73 & Source table does not print temperature; user confirmed the condition matches. \\
R18 & pentose branch & arabinose; 55~$^\circ$C; 3~h; +US & available: direct exact & 74.98 $\pm$ 1.41 & Source table does not print temperature; user confirmed the condition matches. \\
R19 & pentose branch & ribose; 55~$^\circ$C; 2~h; +US & available: direct exact & 71.19 $\pm$ 1.67 & Supplemented from ELISA-2026.6.15.xlsx as ribose 55 C 2 h +US. \\
R20 & pentose branch & ribose; 55~$^\circ$C; 3~h; +US & available: direct exact & 79.04 $\pm$ 0.36 & Source table does not print temperature; user confirmed the condition matches. \\
R21 & heated no-sugar control & no sugar; 55~$^\circ$C; 2~h; +US & available: direct exact & 15.47 $\pm$ 4.79 & Supplemented from ELISA-2026.6.15.xlsx as no-sugar 55 C 2 h +US. \\
R22 & heated no-sugar control & no sugar; 55~$^\circ$C; 3~h; +US & available: direct exact & 20.15 $\pm$ 3.71 & Supplemented from ELISA-2026.6.15.xlsx as no-sugar 55 C 3 h +US; the Chinese condition text repeats 2 h, but the sample label and user confirmation specify 3 h. \\
R23 & heated no-sugar control & no sugar; 55~$^\circ$C; 4~h; +US & available: direct exact & 25.94 $\pm$ 3.13 & Direct match to the planned 24-run condition. \\
R24 & heated no-sugar control & no sugar; 60~$^\circ$C; 4~h; +US & available: direct exact & 35.97 $\pm$ 1.63 & Direct match to the planned 24-run condition. \\
\end{longtable}
\begin{flushleft}
\scriptsize All 24 planned conditions now have directly attributable result records. The seven records previously treated as unavailable (R09--R12, R19, R21 and R22) were supplied in the supplemental workbook \texttt{ELISA-2026.6.15.xlsx}. Reduction values are IgG-binding reductions relative to the untreated baseline and are shown as mean $\pm$ error where available. US, ultrasound pretreatment.
\end{flushleft}
\endgroup
